Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-22 paper/icml_drau/framework.tex

A necessary condition for robustness of an algorithm for
near-continuous time MDPs is 
to remain viable when $\deltat \rightarrow 0$. Thus we will try to
make sure the various quantities involved converge to meaningful
limits when $\deltat\to 0$. \TODO{Formal statements are made in the following section. Proofs and technical assumptions can be found in the supplementary material.}

@@

The definition~\eqref{eq:def-gamma} of the decay factor $\gamma_\deltat$ in
near-continuous environments keeps the time horizon constant in
\emph{physical} time, by making $\gamma_\deltat$ close to $1$ in
algorithmic time. Indeed, physical time horizon is $\deltat$ times the
algorithmic time horizon, namely
\begin{equation}
          \label{eq:time-horizon}
          \frac{\deltat}{1-\gamma^\deltat}
          %= - \frac{1}{\log \gamma} + \bigO(\deltat)
          \approx \frac{1}{1-\gamma},
        \end{equation}
which is thus stable when $\deltat\to 0$. \TODO{We need to add that $\gamma$ is close to 1}
On the other hand,
if $\gamma_\deltat$ was left constant
as $\deltat$ goes to $0$, the corresponding time horizon in physical time
would be $\approx \frac{\deltat}{1 - \gamma}$ which goes to $0$ when
$\deltat$ goes to $0$: such an agent would be increasingly short-sighted
as $\deltat\to 0$.

@@

When the timestep tends to $0$, one converges to the other.
  \begin{theorem}
    \label{th:conv-value}
    Assume that $r: {\cal S} \times {\cal A} \rightarrow \bb R$ is bounded, and
    that $s \rightarrow r(s, \pi(s))$ is lipschitz continuous, then
    for all $s \in {\cal S}$, one has
    %\begin{equation}
    %\label{eq:conv-value}
    $V^\pi_\deltat(s) = V^\pi(s) + \smallo(\deltat)$
    %\end{equation}
    when $\deltat\to 0$.
  \end{theorem}

>>>>

A necessary condition for robustness of an algorithm for
near-continuous time MDPs is 
to remain viable when $\deltat \rightarrow 0$. Thus we will try to
make sure the various quantities involved converge to meaningful
limits when $\deltat\to 0$. The proofs and technical assumptions for the
formal statements below can be found in the supplementary material.

@@

The definition~\eqref{eq:def-gamma} of the decay factor $\gamma_\deltat$ in
near-continuous environments keeps the time horizon constant in
\emph{physical} time, by making $\gamma_\deltat$ close to $1$ in
algorithmic time. Indeed, physical time horizon is $\deltat$ times the
algorithmic time horizon, namely
\begin{equation}
          \label{eq:time-horizon}
          \frac{\deltat}{1-\gamma^\deltat}
          %= - \frac{1}{\log \gamma} + \bigO(\deltat)
          \approx \frac{1}{1-\gamma},
        \end{equation}
which is thus stable when $\deltat\to 0$. 
On the other hand,
if $\gamma_\deltat$ was left constant
as $\deltat$ goes to $0$, the corresponding time horizon in physical time
would be $\approx \frac{\deltat}{1 - \gamma}$ which goes to $0$ when
$\deltat$ goes to $0$: such an agent would be increasingly short-sighted
as $\deltat\to 0$.

@@

When the timestep tends to $0$, one converges to the other.
  \begin{theorem}
    \label{th:conv-value}
    Assume that $r: {\cal S} \times {\cal A} \rightarrow \bb R$ is bounded, and
    that $s \mapsto r(s, \pi(s))$ is lipschitz continuous. Then
    for all $s \in {\cal S}$, one has
    %\begin{equation}
    %\label{eq:conv-value}
    $V^\pi_\deltat(s) = V^\pi(s) + \smallo(\deltat)$
    %\end{equation}
    when $\deltat\to 0$.
  \end{theorem}
